Tree size, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2019-09-19 manuscript/climate_sensitivity_draft.Rmd
removed H1.1b
not significant, not an appropriate test (because height is calculated from DBH).

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("tables_figures/hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(hypothesis_table, booktabs = TRUE, caption = "**Table 1. Summary of hypotheses, corresponding specific predictions, and results.** We count predictions as fully supported / rejected when the response matches/contradicts the prediction in both univariate and multivariate models (when applicable). Parentheses indicate that predictions were partially supported/ rejected--i.e., that the direction of response matched/contradicted the prediction in some but not all models.") %>%
  pack_rows("H1.0. Larger-diameter trees have lower drought resistance.", 1, 1, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H1.1. Drought resistance decreases with tree height.", 2, 3, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H1.2. Drought resistance decreases with crown exposure.", 4, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H1.3. Small trees (lower root volume) suffer more in drier microhabitats.", 6, 6, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H2.1. Species traits predict drought resistance.", 7, 11, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("H2.2. Taller trees have more drought-resistant traits.", 12, 16, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H2.3. Size-dependent drought resistance is not driven by functional traits.", 17, 17, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H3.1. Responses varied by drought.", 18, 18, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("H3.2. Predictor variables varied across droughts.", 19, 20, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  add_header_above(c(" ", "Prediction supported?" = 4, " ")) %>%
  column_spec(1, width = "12cm") %>%
  column_spec(2:5, width = "1cm") %>%
  column_spec(6, width = "2cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 8.5) %>%
  kableExtra::landscape()
```

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("tables_figures/hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(hypothesis_table, booktabs = TRUE, caption = "**Table 1. Summary of hypotheses, corresponding specific predictions, and results.** We count predictions as fully supported / rejected when the response matches/contradicts the prediction in both univariate and multivariate models (when applicable). Parentheses indicate that predictions were partially supported/ rejected--i.e., that the direction of response matched/contradicted the prediction in some but not all models.") %>%
  pack_rows("H1.0. Larger-diameter trees have lower drought resistance.", 1, 1, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H1.1. Drought resistance decreases with tree height.", 2, 2, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H1.2. Drought resistance decreases with crown exposure.", 3, 4, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H1.3. Small trees (lower root volume) suffer more in drier microhabitats.", 5, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H2.1. Species traits predict drought resistance.", 6, 10, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("H2.2. Taller trees have more drought-resistant traits.", 11, 15, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H2.3. Size-dependent drought resistance is not driven by functional traits.", 16, 16, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("H3.1. Responses varied by drought.", 17, 17, latex_gap_space = "1em", colnum = 1, hline_before = TRUE) %>%
  pack_rows("H3.2. Predictor variables varied across droughts.", 18, 19, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  add_header_above(c(" ", "Prediction supported?" = 4, " ")) %>%
  column_spec(1, width = "12cm") %>%
  column_spec(2:5, width = "1cm") %>%
  column_spec(6, width = "2cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 8.5) %>%
  kableExtra::landscape()
```
